A subjective Bayesian framework for synthesizing deep uncertainties in climate risk management

### 2022-07-09 papers/earths-future/submission.tex
update the doi in the paper

All code, including source code, is available under the GNU Public License (version 3) at \url{https://github.com/jdossgollin/2022-elevation-robustness}.
This code is written in the open source Julia programming language and detailed instructions for reproducing our results are provided.
A permanent, citeable archive of the precise version of the codes used in this study is also available on Zenodo at \url{https://doi.org/10.5281/zenodo.6799457}. % Update as needed

>>>>

All code, including source code, is available under the GNU Public License (version 3) at \url{https://github.com/jdossgollin/2022-elevation-robustness}.
This code is written in the open source Julia programming language and detailed instructions for reproducing our results are provided.
A permanent, citeable archive of the precise version of the codes used in this study is also available on Zenodo at \url{https://doi.org/10.5281/zenodo.6814588}.
